\titleformat Exhaustive Search of Binary Code Generator for Solving Non\\Interactive Ulam's Searching Problem with Many Lies

### 2018-07-30 src/tex/paper-isst.tex
udah beres revisi sama paper

%\usepackage{xparse}
\usepackage{amsmath}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{amssymb}
\usepackage{caption}
\usepackage{exscale}
\usepackage{fontspec} 
\usepackage{graphicx}
\usepackage{fancyvrb}
\usepackage{hyperref}
\usepackage{subfigure}
\usepackage{times}
\usepackage{xesearch}

@@

\title{\titleformat Perfect Queries for Non-interactive\\Ulam Searching Game with Many Lies}

@@

\abstractformat{Abstract.}
On the classic Ulam and Rényi searching problem, the questioner has to ask some yes-no questions to find an unknown value within the agreed search space, but the answerer is allowed to lie.
There are already solutions of some variations in the Ulam and Rényi searching problem, i.e. on the type of query between range or subset and the maximum number of lies between one, two, three, and so on.
But there is no perfect solution for non-interactive queries which the answerer can only answer the questioner's query after the questioner has finished querying all the queries.
No research has resolved this problem yet.
In this paper we will describe the perfect solution for non-interactive Ulam and Rényi searching problem with many lies using binary code with Hamming distance.
The algorithm results in this paper show a much smaller number of queries than the common binary repetition algorithm and the best results on a reputable online judge.

\section{Introduction}
% \vspace{-6pt}

@@

@@

\section{Backround of binary code}

@@

The linear code is the most studied code because the algebraic structure is easy to learn compared to the non-linear code \cite{Huffman}. The linear code field can be denoted as $\mathbb{F}_q^n$, ie the code has $q$ element type and has a length of $n$. The binary code form is $\mathbb{F}_2^n $, has the following addition and subtraction algebraic structure.

\begin{align*}
0 + 0 &= 0 & 0 \cdot 0 &= 0 \\
0 + 1 &= 1 & 0 \cdot 1 &= 0 \\
1 + 0 &= 1 & 1 \cdot 0 &= 0 \\
1 + 1 &= 0 & 1 \cdot 1 &= 1
\end{align*}

Hamming distance between two bitstrings $\vec{x}$ and $\vec{y}$ with the same length $n$ is defined by Eq.~\ref{eq:dh}. For example, $d_H(0000,1111)= 4$ and $d_H(00110,00101)= 2$. $d_H(\vec{x},\vec{y})$ can also be defined as the minimum transformation to change $\vec{x}$ to $\vec{y}$. For example, $\vec{x}=00110$ and $\vec{y}=00101$, have two different on the last bits with Hamming distance 2, can also be said $\vec{x}+00011 = \vec{y}$.

\begin{equation} \label{eq:dh}
d_H(\vec{x},\vec{y}) = |\{i \in {1,\ldots,n} \mid x_i \neq y_i\}|
\end{equation}

Weight of bitstring $\vec{x}$ defined with $wt(\vec{x})$, that is number of digits of $\vec{x}$ which is not $0$ as defined by Eq.~\ref{eq:wt}. For example, $wt(00101) = 2$ and $wt(11111) = 5$. Jika dihubungkan dengan jarak Hamming, jika $\vec{x}+\vec{e} = \vec{y}$ maka $d_H(\vec{x},\vec{y}) = wt(\vec{x}+\vec{y})$.

\begin{equation} \label{eq:wt}
wt(\vec{x}) = |\{i \in {1,\ldots,n} \mid x_i \neq 0\}|
\end{equation}

There is an Euclidean metric in the Euclidean space requirement known as triangle inequality \cite{VanLint2016}. From Eq.~\ref{eq:dh_unequal}, assuming $\vec{z}$ is a zero vector $\vec{0}$, then Eq.~\ref{eq:wt_unequal} is obtained.

\begin{align}
d_H(\vec{x},\vec{y}) &\le d_H(\vec{x},\vec{z}) + d_H(\vec{y},\vec{z}) \label{eq:dh_unequal} \\
wt(\vec{x}+\vec{y}) &\le wt(\vec{x}) + wt(\vec{y}) \label{eq:wt_unequal}
\end{align}

\noindent \textbf{Binary Code.}
Binary code is a collection of $M$ binary bitstrings with length $n$ and Hamming distance between every two different bitstrings are maximum $d$. Example $M=8$, $n=6$, and $d=3$ in Fig.~\ref{fig:binarycode683}. Parameter in this binary code is $(6,8,3)_2$, binary is shown by number 2, bitstring length 6, contains 8 bitstrings, and minimum Hamming distance 3. Bitstring in binary code hereinafter called codeword.

\begin{figure}
\centering
\begin{BVerbatim}
000000  100110
001011  101101
010101  110011
011110  111000
\end{BVerbatim}
\caption{Kode biner $(6,8,3)_2$}
\label{fig:binarycode683}
\end{figure}

@@

General notation of binary code is $(n,M,d)_2$. We can assume there are $M$ balls with radius $e$ that are not intersecting each others as in Fig.~\ref{fig:codewordsball}. Distance between one ball to another is at least $d$, so that we can obtain Eq.~\ref{eq:de}.

@@

Now again see a generator matrix $[7,3,4]_2$ in Figure \ref{fig:generator734} can create a perfect binary code $(7,8,4)_2$ code in Figure \ref{fig:binarycode784}. A generator matrix $[n, m, d]_2$ where $n = 2^m - 1$ and each \textbf{column} is all possible $m$ bits binary strings except $\vec{0}$ can make a perfect binary code $(n,M,d)_2$ where $d = M/2$.
\textbf{\textit{We need a proofing or citation..}}

\begin{figure}
\centering
\begin{BVerbatim}
1001101
0101011
0010111
\end{BVerbatim}
\caption{Generator matrix $[7,3,4]_2$}
\label{fig:generator734}
\end{figure}

\begin{figure}
\centering
\begin{BVerbatim}
0000000  1000111
0011101  1000111
0101011  1000111
0110110  1000111
\end{BVerbatim}
\caption{Perfect binary code $(7,8,4)_2$}
\label{fig:binarycode784}
\end{figure}

@@

@@

Fig.~\ref{fig:hamming1} shows an illustration if $M = 8$, $n = 3$, and $d = 1$. The table in the picture shows the Hamming distance between codeword $x$ and $y$, so it can be concluded that the minimum Hamming distance is 1. Fig.~\ref{fig:hamming2} is addition of two codes from Fig.~\ref{fig:hamming1} so that $n = 5$ and $d = 2$.

\begin{figure}
\centering
\includegraphics[scale=0.7]{../img/hamming1.png}
\caption{Hasil tabel jarak Hamming pada $(3,8,1)_2$}
\label{fig:hamming1}
\end{figure}

\begin{figure}
\centering
\includegraphics[scale=0.7]{../img/hamming2.png}
\caption{Hasil tabel jarak Hamming pada $(5,8,2)_2$}
\label{fig:hamming2}
\end{figure}

\section{Summary}
\noindent If you follow the `checklist` your paper will conform to the requirements
 of the publisher and facilitate a problem-free publication process.

>>>>

%\usepackage{xparse}
\usepackage{amsmath}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{amssymb}
\usepackage{caption}
\usepackage{exscale}
\usepackage{fontspec} 
\usepackage{graphicx}
\usepackage{fancyvrb}
\usepackage{hyperref}
\usepackage{subfigure}
\usepackage{times}
\usepackage{xesearch}
\usepackage{tikz}
\usepackage{pgfplots}

\usetikzlibrary{backgrounds}
\usetikzlibrary{shapes.geometric, arrows}
\usetikzlibrary{automata,positioning}

@@

\title{\titleformat Exhaustive Search of Binary Code Generator for Solving Non\\Interactive Ulam's Searching Problem with Many Lies}

@@

\abstractformat{Abstract.}
On the classic Ulam and Rényi searching problem, the questioner has to ask some yes-no questions to find an unknown value within the agreed search space, but the answerer is allowed to lie.
There are already solutions of some variations in the Ulam and Rényi searching problem, i.e. on the type of query between range or subset and the maximum number of lies between one, two, three, and so on.
But there is no perfect solution for non-interactive queries which the answerer can only answer the questioner's query after the questioner has finished querying all the queries.
No research has resolved this problem yet.
In this paper we will describe the perfect solution for non-interactive Ulam and Rényi searching problem with many lies using greedy exhaustive search to generate binary code with Hamming distance.
The algorithm results in this paper show a much smaller number of queries than the common binary repetition algorithm.

\section{Introduction}

@@

There haven't been discussion of Ulam problem with non-interactive queries and more than one lie number, which the questioner must prepare all of his queries before the answerer answer all the query requests at once. The solution generated from this problem can be used to create error correctiong encoding for sending data over a noisy channel, ie when $M$ maca data is sent, there may be an error $e$ bits.

@@

\section{Backround of Binary Code}

@@

Binary code is a collection of $M$ binary bitstrings with length $n$ and Hamming distance between every two different bitstrings are maximum $d$. Example $M=8$, $n=6$, and $d=3$ in Fig.~\ref{fig:binarycode683}. Parameter in this binary code is $(6,8,3)_2$, binary is shown by number 2, bitstring length 6, contains 8 bitstrings, and minimum Hamming distance 3. Bitstring in binary code hereinafter called codeword. General notation of binary code is $(n,M,d)_2$.

\begin{figure}
\centering
\begin{BVerbatim}
000000  100110
001011  101101
010101  110011
011110  111000
\end{BVerbatim}
\caption{Binary code $(6,8,3)_2$}
\label{fig:binarycode683}
\end{figure}

@@

% We can assume there are $M$ balls with radius $e$ that are not intersecting each others. Distance between one ball to another is at least $d$, so that we can obtain Eq.~\ref{eq:de}.

@@

@@

\section{Greedy Exhaustive Search}

@@

The solution using the matrix generator should make a certain $s$ sequence such that a minimum number of $n$ queries generated from $\vec{s}= \{s_1,\ldots,s_n\}$ will generate as many as possible Hamming distance $d$. For that reason, a greedy exhaustive search is proposed to get the most optimized $\vec{s}$ sequences. The greedy approach is used because the global optimum sought is as many as possible the minimum distance value with as few queries as possible. Global optimum can be obtained by finding local optimum in each iteration.

In the greedy algorithm, there are four kinds of selection functions to select the best query candidate on each iteration:
\begin{enumerate}
  \item The most minimum distance;
  \item The most minimum distance, then the least maximum distance;
  \item The most {maximum distance - minimum distance};
  \item The most minimum distance, then the least min count distance.
\end{enumerate}

The four selection functions are determined because the global optimum sought is the largest minimum distance, the difference between the maximum distance and minimum distances should be as small as possible, and the resulting query can eliminate as much as possible the number with minimum distance. The four selection functions will be tested to choose the best selection function and used in the main greedy exhaustive search algorithm.

\section{Testing and Evaluation.}

The testing phase is to test the dataset according to the limit of the problem to find out the results and the performance of the algorithm. Testing will also be used to compare the number of queries, execution time, and memory of the algorithm from all dataset test cases. The dataset will be varied according to the $2 \le M \le 4096$ search space and the maximal $2 \le e \le 16$ lies.

In testing four gredy selection functions, the result shows the number of queries from each selection function, the less the query in all test cases the better. The greedy algorithm with four variations of the selection function will be compared with the bin truth binary repetition algorithm. The result of binary repetition algorithm will also be the maximum query limit, if the number of queries resulted in greedy algorithm exceeds the number of query result of binary repetition, then the number of binary repetition query to be selected.

\begin{figure}
	\centering
	\begin{tikzpicture}
	\begin{axis}[
	xlabel={Jumlah maksimal bohong $e$},
	ylabel={Jumlah query},
	legend pos=north west,
	grid style=dashed,
	legend entries={1,2,3,4,5},
	]
	\addplot[green,mark=*] table{data/brute-min.dat};
	\addplot[red,mark=o] table{data/brute-min-max.dat};
	\addplot[blue,mark=o] table{data/brute-max-min.dat};
	\addplot[purple,mark=*] table{data/brute-min-mincount.dat};
	\addplot[black,mark=o] table{data/brute-repetition.dat};
	\end{axis}
	\end{tikzpicture}
	\caption{Testing of selection function greedy algorithm}
	\label{fig:graph_selection_function}
\end{figure}

\begin{figure}
	\centering
	\begin{tikzpicture}
	\begin{axis}[
	xlabel={Jumlah ruang pencarian($2^m$)},
	ylabel={Waktu eksekusi(detik)},
	legend pos=north west,
	grid style=dashed,
	legend entries={Pengulangan biner,Kode biner,Tabel pencarian},
	]
	\addplot[blue,mark=triangle] table{data/timeR.dat};
	\addplot[red,mark=*] table{data/timeB.dat};
	\addplot[green,mark=square] table{data/timeL.dat};
	\end{axis}
	\end{tikzpicture}
	\caption{Grafik perbandingan waktu eksekusi}
	\label{fig:graph_time}
\end{figure}

\begin{figure}
	\centering
	\begin{tikzpicture}
	\begin{axis}[
	xlabel={Jumlah ruang pencarian($2^m$)},
	ylabel={Penggunaan memory(byte)},
	legend pos=north west,
	grid style=dashed,
	legend entries={Pengulangan biner,Kode biner,Tabel pencarian},
	]
	\addplot[blue,mark=triangle] table{data/memoryR.dat};
	\addplot[red,mark=*] table{data/memoryB.dat};
	\addplot[green,mark=square] table{data/memoryL.dat};
	\end{axis}
	\end{tikzpicture}
	\caption{Grafik perbandingan penggunaan memory}
	\label{fig:graph_memory}
\end{figure}

In Fig.~\ref{fig:graph_selection_function}, legends number one to five are respectively the largest minimum distance, the largest minimum distance then the smallest maximum distance, the maximum distance reducted with the smallest minimum distance, the largest minimum distance then the number of numbers has the smallest minimum value, and last is binary repetition algorithm. From the figure it can be concluded that the most optimal selection function is the largest minimum followed by the number of numbers has the smallest minimum value and the selection function is used in the main greedy exhaustive search algorithm.

In the test of execution time and memory usage, on each algorithm, tested 12 test cases according to the number of search space variations $M = 2^m \mid 1 \leq m \leq 12$. In each test case, there is 15 test cases according to the maximum lie variation $2 \leq e \leq 16$. The test results are shown in Fig.~\ref{fig:graph_time} and Fig.~\ref{fig:graph_memory}. It can be concluded that binary code algorithm without search table resulted in a higher execution time and memory usage, while for binary repetition and binary code with lookup table result in stable execution time and memory usage. This is because the binary code algorithm without the lookup table has the complexity of $O(M^3) $ in the exhaustive search process, whereas the binary code algorithm with the lookup table has the $O(1)$ complexity because the exhaustive search process is done as a pre-process.

\section{Conclusion}
\noindent The conclusion is that the generating binary code with greedy exhaustive search algorithm with greedy selection function used is the largest minimum followed by the number of numbers has the smallest minimum value shows much better results in terms of the number of queries produced, but the execution time and memory usage. Therefore, binary code algorithm can be optimized with lookup table as preprocess so that it can reduce and stabilize the execution time.
